RSA + Scalar implicature / TBD

### 2015-11-30 models/RSA+AmbiguousSemantics.Rmd
prag listener distributional differences update

---
title: "RSA + Scalar implicature / TBD"
author: "BPeloquin/MFrank"
date: "October 29, 2015"
output:
  html_document:
    highlight: pygments
    theme: flatly
    toc: yes
    toc_depth: 2
---
```{r load_data, results="hide", message=FALSE, warning=FALSE}
rm(list = ls())
setwd("/Users/benpeloquin/Desktop/Projects/scalar_implicature/models")
library(tidyr)
source("../analysis/useful_dplyr.R")
library(dplyr)
library(rjson)
library(ggplot2)
library(MASS)
library(jsonlite)

@@

>>>>

---
title: "RSA + Scalar implicature / TBD"
author: "BPeloquin/MFrank"
date: "October 29, 2015"
output:
  html_document:
    highlight: pygments
    theme: flatly
    toc: yes
    toc_depth: 3
---
```{r load_data, results="hide", message=FALSE, warning=FALSE}
rm(list = ls())
setwd("/Users/benpeloquin/Desktop/Projects/scalar_implicature/models")
library(tidyr)
source("../analysis/useful_dplyr.R")
library(dplyr)
library(rjson)
library(ggplot2)
library(MASS)
library(jsonlite)
```

@@

### Pragmatic Listener studies - judgement distributional differences
```{r}
e6.d = read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L1_e6.csv")
e11.d = read.csv("~/Desktop/Projects/scalar_implicature/models/model_data/L1_e11.csv")
match_scales = which((e11.d[, "scale"] != "some_all" &
        (e11.d[, "degree"] == "hi2" | e11.d[, "degree"] == "hi1")) |
       (e11.d[, "scale"] == "some_all" &
          (e11.d[, "degree"] == "hi1" | e11.d[, "degree"] == "low1")))
e11.d.mod = e11.d[match_scales,]
e11.d.mod$degree = ifelse(e11.d.mod$degree == "hi1", "hi", "low")
e11.d.mod = e11.d.mod %>%
  dplyr::select(degree, scale, stars, listener.p) %>%
  mutate(exp = "e11")
e6.d = e6.d %>% mutate(exp = "e6")
combined.d = rbind(e6.d, e11.d.mod)

ggplot(combined.d, aes(x=stars, y=listener.p, fill=exp)) +
  geom_bar(stat="identity", position="dodge") +
  facet_wrap(~scale+degree) +
  ggtitle("e6 vs e11 prag listener judgements")
```
